Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-07-23 document/ms.tex
Add copious references to the previous studies of LkCa4 paragraph of the introduction, maybe too many references.

Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep{harrison11,davenport15}.  Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{bouvier95,grankin07} can break the degeneracy between starspot areal filling factor and starspot temperature. Photometric measurements are limited to detecting the largest longitudinally asymmetric starspots.  Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.  Zeeman Doppler Imaging (ZDI, \emph{e.g.} \citet{donati14}) suffers from the same longitudinally-asymmetric limitation as photometry, but yields information on the latitudinal distribution of starspots.  All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g. bands), or stars with an isotropic distribution of small starspots.

@@

The WTTS \name is an ideal exemplar for a spotted pre-MS star because it has no close companion (cite Kraus, etc.), demonstrates large amplitude sinusoidal photometric variability indicative of spots (cite Grankin), has recently been examined with ZDI (cite Donati), and has large (dTeff~500 K) disagreement about its effective temperature (cite Herczeg and Hillenbrand).  In this work we constrain the starspot properties of \name with 4 complementary techniques.  Section 2 and Appendix YY describe a spectral inference technique aimed at generalizing line depth ratio analysis.  Section 3 applies the spectral inference technique to a high resolution panchromatic near-IR spectrum of \name.  Sections 4.1, 4.2, and 4.3 show results from polychromatic photometric monitoring analysis, SED fitting, and optical TiO line-depth ratio fitting.  All lines of evidence are ultimately combined to build a (in?)harmonious picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.

\todo{Discuss limitations and capabilities of photometry alone: presence or absence of starspots, joint constraint on areal coverage and temperature, longitudinal asymmetry.}
Cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots \citep{harrison12}.  Photometric modeling of the light curve taken alone can only yield degenerate estimates in the temperature contrast and areal coverage fraction.  A star possessing longitudinally symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating (or very slowly rotating) star would all show zero or secular amplitude of photometric variability, yet they all contain star spots.

By modeling the composite spectrum of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.  Spectroscopic modeling can still measure the starspot properties in pole-on stars, stars with longitudinally symmetric stars, and non-rotating stars.

\todo{Cite previous efforts to derive starspot properties via spectroscopy}

\todo{More advanced approaches to understanding stellar surface properties.  How many distinct spot groups are there?  Is there evidence for both hot spots and cool spots?  What is the longitudinal distribution of the spots?  What is the (co-)latitudinal distribution of the spots?  What is the distribution of effective temperature within a spot or spot group?  What are the morphologies of the spots?}
In principle, more advanced questions could be asked about the properties of the spots....

Solving these questions would require a complex model comparison framework, combining all available data and lines of evidence from photometric, spectroscopic, and spectropolarimetric monitoring.  We seek to answer the much easier questions about the aggregate properties of the stellar photosphere, assuming the star is well described by two distinct photospheric components.

\todo{Previous studies of \name}

In this paper we characterize the starspot coverage and temperature contrast of \name by fitting photospheric models to high-resolution optical and near-IR spectra.  We chose \name for its likelihood of large areal coverage of starspots, as seen in large-amplitude photometric variability  detected in $BVRI$ bands with a period is 3.37$\pm$0.01 days \citep{vrba93,grankin94,grankin08,xiao12}.  Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{donati14}.

%This statement needs to be fact-checked, maybe some more supporting info.

Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.  \name does not have any mid-IR or mm excess \citep[e.g.][]{furlan06}, is not actively accreting (ref?), and does not have any known companion (some Kraus? paper).  The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.

We extend a new spectral forward modeling framework to include two-temperature photosphere models.  We demonstrate the constraining power of full spectrum fitting with panchromatic optical and near-IR echelle spectroscopy.
% Consider putting in Section references here

>>>>

Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep{harrison11,davenport15}.  Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{bouvier95,grankin07} can break the degeneracy between starspot areal filling factor and starspot temperature. Photometric measurements are limited to detecting the largest longitudinally asymmetric starspots.  Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.  Zeeman Doppler Imaging (ZDI, \emph{e.g.} \citet{donati14}) suffers from the same longitudinal asymmetry limitation as photometry, but can yield information on the latitudinal distribution of starspots.  All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g. bands), or stars with an isotropic distribution of small starspots.

@@

Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.  The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep{hartigan95,kenyon98,edwards06,cauley12,yang12,ardila13,castro13,loyd14,martinez15}, has no evidence for a close companion \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11}}, demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}, has recently been examined with ZDI \citep{donati14}, and has large ($\delta \teff \sim$500 K) disagreement about its effective temperature \citep{herczeg14}.  The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.

In this work we constrain the starspot properties of \name with 4 complementary techniques.  Section 2 and Appendix YY describe a spectral inference technique aimed at generalizing line depth ratio analysis.  Section 3 applies the spectral inference technique to a high resolution panchromatic near-IR spectrum of \name.  Sections 4.1, 4.2, and 4.3 show results from polychromatic photometric monitoring, SED fitting, and optical TiO line-depth ratio fitting.  All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
